{ \fontfamily{ptm}\selectfont Catalyst Meta Acceleration Framework: The history and the gist of it }

### 2024-11-12 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, syncing

\section{Preliminaries}\label{sec:preliminaries}
    Throughout the writing, let the ambient space is $\RR^n$. 
    The optimization problem is
    \begin{align*}
        \min_{x \in \RR^n} F(x). 
    \end{align*}
    This section introduces the Nesterov's estimating sequence technique. 
    This technique is fundamental for in Guler's accelerated PPM method and Catalyst meta acceleration in the convex/strongly convex case. 
    \subsection{Method of Nesterov's Estimating Sequence}
        \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
            Let $(\phi_k : \RR^n \mapsto \RR)_{k \ge 0}$ be a sequence of functions. 
            We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions that: 
            \begin{enumerate}
                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*$. 
                \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ such that for all $x \in \RR^n$, $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$. 
            \end{enumerate}
        \end{definition}
        \begin{observation} 
            If we define $\phi_k$, $\Delta_k(x) := \phi_k (x) - F(x)$ for all $x \in \RR^n$ and assume that $F$ has minimizer $x^*$. 
            Then observe that $\forall k \ge 0$:  
            \begin{align*}
                \Delta_k(x) 
                &= \phi_k(x) - f(x) \ge \phi_k^* - f(x)
                \\
                x = x_k\implies 
                \Delta_k(x_k) 
                &\ge 
                \phi_k^* - f(x_k) \ge 0
                \\
                x = x_* \implies 
                \Delta_k(x_*)
                &\ge \phi_k^* - f_* \ge f(x_k) - f_* \ge 0
            \end{align*}
            The function $\Delta_k(x)$ is non-negative at points: $x_*, x_k$.
            We can derive the convergence rate of $\Delta_k(x^*)$ because $\forall x \in \RR^n$: 
            \begin{align*}
                \phi_{k + 1}(x) - \phi_k(x) 
                &\le - \alpha_k (\phi_k(x) - F(x))
                \\
                \iff 
                \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
                &\le 
                -\alpha_k(\phi_k(x) - F(x))
                \\
                \iff
                \Delta_{k + 1}(x) - \Delta_k(x) &\le
                - \alpha_k\Delta_k(x)
                \\
                \iff 
                \Delta_{k + 1}(x) 
                &\le 
                (1 - \alpha_k)\Delta_k(x). 
            \end{align*}
            Unrolling the above recursion it yields: 
            \begin{align*}
                \Delta_{k + 1}(x) &\le 
                (1 - \alpha_k)\Delta_k(x) \le \cdots \le 
                \left(
                    \prod_{i = 0}^k(1 - \alpha_i)
                \right)\Delta_0(x). 
            \end{align*}
            Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using the property of Nesterov's estimating sequence it gives: 
            $$
                f(x_k) - f(x^*) \le \phi_k^* - f(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - f(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).
            $$ 
        \end{observation}
        Creativity is important in the construction of the estimating sequence $(\phi_k)_{k \ge 0}$.

@@

            & \text{find } \alpha_{k + 1} \in (0, 1)

>>>>

\section{Preliminaries}\label{sec:preliminaries}
    Throughout the writing, let the ambient space is $\RR^n$. 
    The optimization problem is
    \begin{align*}
        \min_{x \in \RR^n} F(x). 
    \end{align*}
    This section introduces the Nesterov's estimating sequence technique. 
    This technique is fundamental for in Guler's accelerated PPM method and Catalyst meta acceleration in the convex/strongly convex case. 
    \subsection{Method of Nesterov's Estimating Sequence}
        \begin{definition}[Nesterov's estimating sequence]\label{def:nes-est-seq}
            Let $(\phi_k : \RR^n \mapsto \RR)_{k \ge 0}$ be a sequence of functions. 
            We call this sequence of function a Nesterov's estimating sequence when it satisfies the conditions that: 
            \begin{enumerate}
                \item There exists another sequence $(x_k)_{k \ge 0}$ such that for all $k \ge 0$ it has $F(x_k) \le \phi_k^*$. 
                \item There exists a sequence of $(\alpha_k)_{k \ge 0}$ such that for all $x \in \RR^n$, $\phi_{k + 1}(x) - \phi_k(x) \le - \alpha_k(\phi_k(x) - F(x))$. 
            \end{enumerate}
        \end{definition}
        \begin{observation} 
            If we define $\phi_k$, $\Delta_k(x) := \phi_k (x) - F(x)$ for all $x \in \RR^n$ and assume that $F$ has minimizer $x^*$. 
            Then observe that $\forall k \ge 0$:  
            \begin{align*}
                \Delta_k(x) 
                &= \phi_k(x) - F(x) \ge \phi_k^* - F(x)
                \\
                x = x_k\implies 
                \Delta_k(x_k) 
                &\ge 
                \phi_k^* - F(x_k) \ge 0
                \\
                x = x_* \implies 
                \Delta_k(x_*)
                &\ge \phi_k^* - F_* \ge F(x_k) - F_* \ge 0
            \end{align*}
            The function $\Delta_k(x)$ is non-negative at points: $x_*, x_k$.
            We can derive the convergence rate of $\Delta_k(x^*)$ because $\forall x \in \RR^n$: 
            \begin{align*}
                \phi_{k + 1}(x) - \phi_k(x) 
                &\le - \alpha_k (\phi_k(x) - F(x))
                \\
                \iff 
                \phi_{k + 1}(x) - F(x) - (\phi_k(x) - F(x))
                &\le 
                -\alpha_k(\phi_k(x) - F(x))
                \\
                \iff
                \Delta_{k + 1}(x) - \Delta_k(x) &\le
                - \alpha_k\Delta_k(x)
                \\
                \iff 
                \Delta_{k + 1}(x) 
                &\le 
                (1 - \alpha_k)\Delta_k(x). 
            \end{align*}
            Unrolling the above recursion it yields: 
            \begin{align*}
                \Delta_{k + 1}(x) &\le 
                (1 - \alpha_k)\Delta_k(x) \le \cdots \le 
                \left(
                    \prod_{i = 0}^k(1 - \alpha_i)
                \right)\Delta_0(x). 
            \end{align*}
            Finally, by setting $x = x^*$, $\Delta_k(x^*)$ is non-negative and using the property of Nesterov's estimating sequence it gives: 
            $$
                F(x_k) - F(x^*) \le \phi_k^* - F(x^*) \le \Delta_k(x^*) = \phi_k(x^*) - F(x^*) \le \left(\prod_{i = 0}^k(1 - \alpha_i)\right)\Delta_0(x^*).
            $$ 
        \end{observation}
        Creativity is important in the construction of the estimating sequence $(\phi_k)_{k \ge 0}$.

@@

            & \text{find } \alpha_{k + 1} \in (0, 1): 
